---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MultidimensionalPovertyPrediction

<!-- badges: start -->
<!-- badges: end -->

The goal of MultidimensionalPovertyPrediction is to ...

## Installation

You can install the development version of MultidimensionalPovertyPrediction from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("girelaignacio/MultidimensionalPovertyPrediction")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r intro}
library(MultidimensionalPovertyPrediction)
## basic example code

target <- "MPI"
which.data <- 1

data <- preprocessing.dataframe(which.data, target, time.format = "trend")

head(data)
```

###### Set parameters for tuning parameters
```{r tuning_parm}
### Set parameters for tuning parameters
n_folds <- 5
n_comp <- 10

```

##### Split train and test data
```{r splitdata}
train_index <- caret::createDataPartition(data[,target], p = 0.8, list = FALSE, times = 1)
data_train <- data[train_index,]
data_test <- data[-train_index,]
ytrain <- data_train[,target] ; Xtrain <- data_train[,-1]
ytest <- data_test[,target] ; Xtest <- data_test[,-1]
```


###### Set train fitting control
```{r set_fitcontrol}
CV_index <- caret::createResample(data[,target])

fitControl <- caret::trainControl(method="cv",
                                  number=n_folds,
                                  index = CV_index)
```

##### Fit a model (PLS with linear model)
```{r pls-lm}
pls_lm.fit <- caret::train(x = Xtrain, y = ytrain, 
                 method = pls_lm, 
                 ncomp = 10,
                 trControl = fitControl,
                 verbose = FALSE)
```

###### Predict!
```{r pls-lm_pred}
ypred <- predict(lm.fit, Xtest)
```

###### Check error
```{r errors}
mean((ytest - ypred)^2)
```
